\chapter*{Contribute to \emph{ELR}}
There are many ways to contribute to the conversation about engineering leadership.

\subsection{Read \& Share}
Once you are done with this issue of \emph{ELR}, pass the copy---be it physical or electronic---on to a friend.
Amongst your coworkers, classmates, labmates, co-faculty and clients, share the link to the \emph{ELR} website:
\begin{center}\url{http://lot.utoronto.ca/review}\end{center}

If physical copies of the issue are desired for distribution at your institution, organization or company, additional printings can be arranged at cost.
Contact the Editors for details.

\subsection{Request}
If there are \emph{topics} about which you would like to read\ldots

Alternately, if you know a distinguished individual or group of engineering leaders, introduce them to us and tell us which of their accomplishments deserves sharing.
The Editorial Board can handle the task of 

\subsection{Review}
\emph{ELR} is a peer-reviewed publication with a double-blind review process.
Unlike technical journals which match `peers' based on subject-area expertise, \emph{ELR} matches based on extent and type of leadership learning and experience.

We need many reviewers for each issue.
Let us know if you are interested in viewing manuscripts and providing detailed comments on style, language, organization, and of course leadership content.

\subsection{Write}
\emph{ELR} accepts a mix of solicited and unsolicited submissions for each issue.

If you have a leadership topic in mind but are unsure of where to start, our Section Editors can assist you in formulating a concept for an article appropriate for \emph{ELR}, suggest how to select and involve coauthors, and provide other assistance.

If, on the other hand, you feel are ready to write, then please consult the \emph{Instructions to Authors} (p.~\pageref{authorguide}).

\emph{ELR} also welcomes commentary and responses to articles published in previous issues.
Commentary may be printed as-is, edited for brevity, shared privately with the original authors, or---if the length is sufficient---published as an article in its own right.

\subsection{Edit}
The members of the \emph{ELR} Editorial Board (p.~\pageref{masthead}) consists mostly of undergraduate and graduate students.
We are seeking to have a mix of individuals whiw
\begin{multicols}{2}
  \begin{itemize}
    \item Academic publishing
    \item Illustration and graphic design
    \item Journalism
    \item Layout design
    \item Marketing \& promotion
    \item Typography
    \item Writing and editing
  \end{itemize}
\end{multicols}
